%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{hyperref}
\usepackage{xcolor}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

\newcommand{\updateinfo}[1][\today]{\par\vfill{\scriptsize\color{gray}Updated on #1}}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Yi J Zhu} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{(301) 250-6398}
\moveleft.5\hoffset\centerline{yi.zhu@berkeley.edu}
\moveleft.5\hoffset\centerline{\url{ocf.berkeley.edu/~yizhu/}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION} 

{\textbf{Harvard University}}\\
 PhD Quantum Science and Engineering \hfill 2022--Present

{\textbf{University of California, Berkeley}}\\
BS Engineering Physics \hfill 2018--2022
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\textbf{Berkeley Trapped Ions Group}} \hfill July 2020 – Present\\
Supervisors: Hartmut H\"{a}ffner, Sara Mouradian
\begin{itemize}
\item Quantum information processing with trapped $^{40}$Ca$^{+}$ ions
\item Simulated and optimized waveguide crossings for integrated photonics.
\item Designed, characterized, and constructed a free-space optical system for single-ion addressing.
\item Simulated sources of field error in trapped-ion systems via IonSim.
\end{itemize}

{\textbf{Ultrafast Nano-Optics Group, UC Berkeley}} \hfill May 2019 - December 2019\\
Supervisors: Feng Wang, Tairu Lyu 
\begin{itemize}
\item Constructed graphene-based heterostructures for detection of thermal waves.
\item Reprogrammed controls for the stamping motor, thermocouple, and Peltier cooler.
\item Performed Raman spectroscopy of trilayer-graphene and analyzed Raman shift.
\end{itemize}

\section{TEACHING\\OUTREACH}

{\textbf{Director, Undergraduate Labs at Berkeley, Physics \& Astronomy Division}}\\
\null \hfill August 2019 – Present
\begin{itemize}
\item Lead instructor for the Undergraduate Lab at Berkeley (ULAB): a 2-semester course that seeks to make research accessible to under-supported students and students traditionally underrepresented in academia.
\item Taught over 150 students and oversee over 30 members of staff conducting projects on topics in physics and astronomy.
\item Designed assignments on Python, LaTeX, Statistics, and Git.
\item Coordinated with advisors, faculty, postdocs, and graduate students in the physics and astronomy departments.
\item Securing department funding and grants. Obtained \$60,000 over 3 years as part of the Berkeley Discover Grant (PI: Eugene Chiang). 
\end{itemize}

{\textbf{BURET Group}} \hfill September 2021 - Present\\
Supervisors: Elisa Stone
\begin{itemize}
    \item The Berkeley Undergraduate Research Evaluation Tool (BURET) group develops tools to evaluate the effectiveness of undergraduate research experiences.
    \item Performing a study of ULAB's effectiveness in promoting accessibility of undergraduate research using novel tools developed by the group.
\end{itemize}

{\textbf{Course Reader}} \\
Grading and correcting homework for:
\begin{itemize}
    \item Physics C191: Quantum Information Science and Technology \hfill Fall 2021
    \item Physics 110A: Electromagnetism and Optics\hfill Spring 2021
    \item Physics 5B: Introductory Electromagnetism, Waves, and Optics \hfill Fall 2020
\end{itemize}

\section{TALKS}
{\textbf{Berkeley Physics Research Fair}} \hfill Spring 2020
\begin{itemize}
    \item \textit{A Scalable Approach to Ion Addressing in a Linear Paul Trap}
\end{itemize}

\section{HONORS}

{\textbf{Berkeley Physics Undergraduate Research Scholarship}} \hfill Spring 2021
\begin{itemize}
    \item Scholarship from the Berkeley Physics department in support of my research with the H\"{a}ffner group.
\end{itemize}


{\textbf{Edward Frank Kraft Scholarship}} \hfill February 2019
\begin{itemize}
    \item Awarded to students who have attained the highest scholastic records in their first semester at UC Berkeley.
\end{itemize}

\section{COURSEWORK}

\begin{itemize}
\item Physics: classical mechanics, electromagnetism and optics (2 semesters), quantum mechanics (3 semesters), solid state (1 semester), quantum information science and technology, general relativity
\item Math: linear algebra, real analysis, complex analysis, statistics
\end{itemize}

\updateinfo

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}