\documentclass{resume}
\usepackage[letterpaper, portrait, margin=1.5cm]{geometry}
\newenvironment{indented}{\vspace{-5pt}\begin{list}{}{\setlength{\leftmargin}{0.5cm}}\item[]}{\end{list}}

\name{Yi Jeffrey Zhu}
\address{2421 Prospect Street, Berkeley, CA, 94704} 
\address{(301) 250-6398 \\ yi.zhu@berkeley.edu}

\begin{document}
	
	\begin{rSection}{Education}
		{\bf University of California, Berkeley} \hfill {\em August 2018 -- Present} 
		\begin{indented}
			B.S. Engineering Physics
			\\Expected Graduation: 2022; GPA: 3.985/4.0
		\end{indented}
	\end{rSection}

	\begin{rSection}{Experience}
		{\bf Director, Undergraduate Labs at Berkeley, Physics \& Astronomy  } \hfill {\em August 2020 -- Present}\\
		{\bf Lab Manager } \hfill {\em August 2019 -- August 2020}
		\begin{indented}
			The Undergraduate Lab at Berkeley (ULAB) is a 2-unit/2-semester course that seeks to make research accessible to inexperienced students and students traditionally underrepresented in academia. As director, I oversee approximately 40 students and over 20 members of staff. Responsibilities include: teaching, advising research projects, coordinating with physics and astronomy department/faculty, and applying for funding.
		\end{indented}
		
		\vspace{-1pt} {\bf Trapped Ions Group, UC Berkeley} \hfill {\em July 2020 -- Present}
		\begin{indented}
			Working on simulating, designing, and implementing a single-ion addressing system. Previously completed a project on simulating and optimizing waveguide crossings. Previously simulated sources of field error in trapped-ion systems via the IonSim package in Julia.
		\end{indented}
		
		
		\vspace{-1pt} {\bf Ultrafast Nano-Optics Group, UC Berkeley} \hfill {\em Summer 2019}
		\begin{indented}
			Aided in the production of graphene-based heterostructures with the goal of detecting the novel condense-matter phenomena of thermal waves: non-diffusive heat propagation. Contributed to the improvement of lab-setup by reprogramming controls for the stamping motor, thermocouple, and Peltier cooler. Performed Raman spectroscopy of trilayer-graphene (3LG) and analyzed Raman shift.
		\end{indented}
	
		\vspace{-1pt} {\bf Vaccine Research Center, Structural Biology Group, NIAID/NIH} \hfill {\em Summer 2016 and 2017}
		\begin{indented}
			Contributed to the Vaccine Research Center's HIV and hPIV vaccine-design process. Created, out of personal initiative, a custom database to track and analyze effective HIV antigens. Conducted x-ray crystallography of hPIV-3 envelope glycoproteins from start to finish: protein expression, purification, crystallization, and diffraction. Personally collected data at the Synchrotron at Argonne National Laboratories.
		\end{indented}
		
		\vspace{-1pt} {\bf National Institutes of Mental Health} \hfill {\em Summer 2015}
		\begin{indented}
			Performed basic laboratory techniques such as western blots and gel-electrophoresis. Assisted the lab on surgical implantation of fiber optics cables in mice for use in an optigenetics study of aggression pathways in the brain associated with Alzheimer's. 
		\end{indented}
	\end{rSection}

	\begin{rSection}{Coursework}
	
	\textbf{Maths}: Linear Algebra, Real Analysis,  Statistics
	\\
	\textbf{Physics}: Analytical Mechanics, Electrodynamics, Quantum Mechanics, Statistical Mechanics, Solid State
	\\
	\textbf{Engineering}: Signals and Systems, Optical Engineering, Fluid Mechanics
	
	\end{rSection}

	\begin{rSection}{Programming Skills}
		
		\textbf{Proficient}: Python, Java
		\\
		\textbf{Additional experience}: Julia, C
		
	\end{rSection}

	\begin{rSection}{Honors and Scholarships}
		{\bf Berkeley Physics Undergraduate Research Scholar (BPURS)} \hfill {\em February 2021}
		\begin{indented}
			My research efforts during the Spring 2021 semester is supported by Berkeley Physics Department under the BPURS program.
		\end{indented}
		{\bf Edward Frank Kraft Scholarship} \hfill {\em February 2019}
		\begin{indented}
			Awarded to UC Berkeley freshmen for academic excellence.
		\end{indented}
	
		\vspace{-1pt} {\bf Full Banneker/Key Scholarship} \hfill {\em March 2018}
		\begin{indented}
			University of Maryland's most prestigious scholarship offered to students who have exhibited ``significant academic leadership and accomplishment."
		\end{indented}
		
		\vspace{-1pt} {\bf Siemens Competition Regional Finalist} \hfill {\em October 2016}
		\begin{indented}
			Project on a novel computational HIV vaccine design method (above) was selected as top 10 out of over 1,600 entries. 
		\end{indented}
	\end{rSection}
\end{document}